Analysis : exp220 - 228 (Nov 2018, for J Neurophys draft 2018)

### 2019-08-21 resistingrhythm/analysis/paper_figures_v4.Rmd
Added new control panels to (now) Fig 4.

## Main gamma
```{r}
# ----------------------------------------------------------------------
# @ 60 Hz, burst
#
# No H
exp_code <- 329
osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
stim_codes <- c(3, 4)

@@

@@

# Figure: Gamma (AMPA)
```{r, fig.height=2.1, fig.width=2.6}
freq_labels <- as_labeller(c('60' = "60 Hz", '90' = "90 Hz"))
gamma_results %>% 
  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
  filter(homeo == "Homeostasis") %>% 
  group_by(freq, osc_rate, kind) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(aes(x=osc_rate, y=M, group=interaction(osc_rate, kind), color=kind)) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=kind), size=.4) +
  geom_point() +
  theme_classic() +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  labs(y="Pop. rate", x="Osc. rate", tag="a.") +
  lims(y=c(0, 100)) +
  theme(legend.position = "right",
        plot.tag = element_text(size=16, face="bold"),
        legend.background = element_rect(colour ="black"),
        panel.spacing = unit(1, "lines"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank()) +
  facet_grid(.~freq, scales = "free", labeller=freq_labels) -> p1

gamma_results %>% 
  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
  filter(homeo == "Homeostasis") %>% 
  group_by(freq, osc_rate, kind) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(aes(x=osc_rate, y=M, group=interaction(osc_rate, kind), color=kind)) +
  geom_point() +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=kind), size=.4) +
  theme_classic() +
  facet_grid(.~freq, scales = "free", labeller = freq_labels) +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  lims(y=c(0.0, .12)) +
  theme(legend.position = "none",
        plot.tag = element_text(size=16, face="bold"),
        panel.spacing = unit(1, "lines"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank()) +
  labs(y="Kappa", x="Osc. rate", tag="b.") -> p2

@@

# Figure: Control
```{r, fig.width=2.4, fig.height=2.8}
# -
results228 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate, Ca_target) %>% 
  summarise(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp1

@@

# -----------------------------------------------------------------------------------
# Frac of tau_h
# rate
rbind(results231, results232) %>% 
  ggplot(aes(x=frac_tau_h, y=rate_k, color=homeo, group=interaction(homeo, frac_tau_h))) +
  geom_boxplot(size=0.6) +
  stat_compare_means(method="wilcox.test", label="p.signif", 
                     label.x=1.3, size=3, show.legend=FALSE) +
  labs(title="c.", y="Pop. rate", x=TeX("$t_{oscillation} / \\tau_{h}$")) +
  scale_color_manual(values=c("black", "grey"), name=NA) +
  theme_classic2() +
  theme(
    plot.title = element_text(hjust = -.5, size=18, face="bold"),
    legend.background = element_rect(colour ="black"),
    legend.position = c(1.35, 0.5),
    legend.title=element_blank(),
    legend.key.size = unit(.3, "cm")) -> p6

# -
p3 <- textGrob("")
p4 <- textGrob("Target [Ca]\nperturbation")
p8 <- textGrob(TeX("Biological $\\tau_h$"))
p5 <- nullGrob()
p9 <- nullGrob()

# -
# layout_matrix <- rbind(
#   c(4, 2, 2, 5), 6, 6, 5),
#   c(4, 2, 2, 5), 6, 6, 5),
#   c(4, 2, 2, 5), 6, 6, 5),
#   c(4, 2, 2, 5), 6, 6, 5),
#   c(3, 1, 1, 5), 7, 7, 5),
#   c(3, 1, 1, 5), 7, 7, 5),
#   c(3, 1, 1, 5), 7, 7, 5), 
#   c(3, 1, 1, 5), 7, 7, 5) 
# )

layout_matrix <- rbind(
  c(4, 2, 2, 5), 
  c(4, 2, 2, 5), 
  c(4, 2, 2, 5), 
  c(4, 2, 2, 5), 
  c(3, 1, 1, 5), 
  c(3, 1, 1, 5), 
  c(3, 1, 1, 5),  
  c(3, 1, 1, 9), 
  c(8, 6, 6, 9),
  c(8, 6, 6, 9),
  c(8, 6, 6, 9),
  c(8, 6, 6, 9)
)
grid.arrange(p1, p2, p3, p4, p5, p6, p8, p9, layout_matrix=layout_matrix)

>>>>

## Gamma
```{r, message=FALSE}
# ----------------------------------------------------------------------
# @ 60 Hz, burst
#
# No H
exp_code <- 329
osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
stim_codes <- c(3, 4)

@@

## Leak
```{r, message=FALSE}
# Main exp
# -----------------------------------------------------------------------
# 15: Sustained E, with H
exp_code <- 221
osc_codes <- c(100, 115)
osc_rates <- c(0, 1.5)
stim_codes <- c(3, 4)

results221b <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$g_L <- rep("1.0e-3", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    df$freq <- rep(8, nrow(df))
    results221b <- rbind(results221b, df)
  }
}

results221b %>%
  filter(rate_k > 0) -> results221b

# ----------------------------------------------------------------------
# gL perturb exps
# H
exp_code <- 317
osc_codes <- c(100, 115)
osc_rates <- c(0, 1.5)
stim_codes <- c(3, 4) # 4
g_Ls <- c("0.9e-3", "0.95e-3", "1.05e-3", "1.1e-3")

results317 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(g in g_Ls){

      # Load the csv
      # exp316_stim{1}_gl{3}_osc
      df <- read_csv(paste(data_path, 
                           "exp", as.character(exp_code), 
                           "_stim", as.character(s_c), 
                           "_gl", as.character(g), 
                           "_osc", as.character(o_c),
                           ".csv", sep=""))

      # Add metadata
      df$osc_code <- rep(o_c, nrow(df))
      df$osc_rate <- rep(o_r, nrow(df))
      df$stim_code <- rep(s_c, nrow(df))
      df$synapse <- rep("AMPA", nrow(df))
      df$g_L <- rep(g, nrow(df))
      df$homeo <- rep("Homeostasis", nrow(df))
      df$freq <- rep(8, nrow(df))

      results317 <- rbind(results317, df)
    }
  }
}
results317 %>%
  filter(rate_k > 0) -> results317

# no H
exp_code <- 316
osc_codes <- c(100, 115)
osc_rates <- c(0, 1.5)
stim_codes <- c(3, 4) # 4
g_Ls <- c("0.9e-3", "0.95e-3", "1.05e-3", "1.1e-3")

results316 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(g in g_Ls){

      # Load the csv
      # exp316_stim{1}_gl{3}_osc
      df <- read_csv(paste(data_path, 
                           "exp", as.character(exp_code), 
                           "_stim", as.character(s_c), 
                           "_gl", as.character(g), 
                           "_osc", as.character(o_c),
                           ".csv", sep=""))

      # Add metadata
      df$osc_code <- rep(o_c, nrow(df))
      df$osc_rate <- rep(o_r, nrow(df))
      df$stim_code <- rep(s_c, nrow(df))
      df$synapse <- rep("AMPA", nrow(df))
      df$g_L <- rep(g, nrow(df))
      df$homeo <- rep("No homeostasis", nrow(df))
      df$freq <- rep(8, nrow(df))

      results316 <- rbind(results316, df)
    }
  }
}
results316 %>%
  filter(rate_k > 0) -> results316

results_control_leak <- rbind(
  results316,
  results317,
  results221b
)

results_control_leak$g_L <- factor(
  results_control_leak$g_L, levels=c("0.9e-3", "0.95e-3", "1.0e-3", "1.05e-3", "1.1e-3"))
```

## Theta drift
```{r, message=FALSE}
# ----------------------------------------------------------------------
# Load 8 Hz theta AMPA
# 16: Burst E, with H
exp_code <- 287
osc_codes <- c(100, 105, 110, 115)
osc_rates <- c(0, 0.5, 1.0, 1.5)
stim_codes <- c(3, 4) # 4

results289 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    df$freq <- rep(8, nrow(df))
    results289 <- rbind(results289, df)
  }
}
results289 %>%
  filter(rate_k > 0) -> results289

# Load 8 Hz theta AMPA
# 16: Burst E, no H
exp_code <- 286
osc_codes <- c(100, 105, 110, 115)
osc_rates <- c(0, 0.5, 1.0, 1.5)
stim_codes <- c(3, 4) # 4

results288 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(8, nrow(df))
    results288 <- rbind(results288, df)
  }
}
results288 %>%
  filter(rate_k > 0) -> results288

# ----------------------------------------------------------------------
# @ 6 Hz
#
# No H
exp_code <- 298
osc_codes <- c(100, 105, 110, 115)
osc_rates <- c(0, 0.5, 1.0, 1.5)
stim_codes <- c(3, 4)

results298 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(6, nrow(df))
    results298 <- rbind(results298, df)
  }
}
results298 %>%
  filter(rate_k > 0) -> results298

# H
exp_code <- 299
osc_codes <- c(100, 105, 110, 115)
osc_rates <- c(0, 0.5, 1.0, 1.5)
stim_codes <- c(3, 4)

results299 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$freq <- rep(6, nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))

    results299 <- rbind(results299, df)
  }
}
results299 %>%
  filter(rate_k > 0) -> results299

# ----------------------------------------------------------------------
# @ 7 Hz
#
# No H
exp_code <- 302
osc_codes <- c(100, 105, 110, 115)
osc_rates <- c(0, 0.5, 1.0, 1.5)
stim_codes <- c(3, 4)

results302 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(7, nrow(df))
    results302 <- rbind(results302, df)
  }
}
results302 %>%
  filter(rate_k > 0) -> results302

# H
exp_code <- 303
osc_codes <- c(100, 105, 110, 115)
osc_rates <- c(0, 0.5, 1.0, 1.5)
stim_codes <- c(3, 4)

results303 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$freq <- rep(7, nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    results303 <- rbind(results303, df)
  }
}
results303 %>%
  filter(rate_k > 0) -> results303

# ----------------------------------------------------------------------
# @ 9 Hz
#
# No H
exp_code <- 306
osc_codes <- c(100, 105, 110, 115)
osc_rates <- c(0, 0.5, 1.0, 1.5)
stim_codes <- c(3, 4)

results306 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(9, nrow(df))
    results306 <- rbind(results306, df)
  }
}
results306 %>%
  filter(rate_k > 0) -> results306

# H
exp_code <- 307
osc_codes <- c(100, 105, 110, 115)
osc_rates <- c(0, 0.5, 1.0, 1.5)
stim_codes <- c(3, 4)

results307 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$freq <- rep(9, nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    results307 <- rbind(results307, df)
  }
}
results307 %>%
  filter(rate_k > 0) -> results307

# ----------------------------------------------------------------------
# @ 10 Hz
#
# No H
exp_code <- 310
osc_codes <- c(100, 105, 110, 115)
osc_rates <- c(0, 0.5, 1.0, 1.5)
stim_codes <- c(3, 4)

results310 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(10, nrow(df))
    results310 <- rbind(results310, df)
  }
}
results310 %>%
  filter(rate_k > 0) -> results310

# H
exp_code <- 311
osc_codes <- c(100, 105, 110, 115)
osc_rates <- c(0, 0.5, 1.0, 1.5)
stim_codes <- c(3, 4)

results311 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$freq <- rep(10, nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    results311 <- rbind(results311, df)
  }
}
results311 %>%
  filter(rate_k > 0) -> results311

# ------------------------------------------------------------------------------------
# Join results
results_control_drift <- rbind(
  results288, 
  results289, 
  results298, 
  results299, 
  results302, 
  results303, 
  results306, 
  results307, 
  results310, 
  results311)
```

@@

# Figure: Gamma (AMPA)
```{r, fig.height=2.1, fig.width=2.6}
freq_labels <- as_labeller(c('60' = "60 Hz", '90' = "90 Hz"))
gamma_results %>% 
  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
  filter(homeo == "Homeostasis") %>% 
  group_by(freq, osc_rate, kind) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=kind)) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=kind), size=.4) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  theme_classic() +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  labs(y="Pop. rate", x="Osc. rate", tag="a.") +
  lims(y=c(0, 100)) +
  theme(legend.position = "right",
        plot.tag = element_text(size=16, face="bold"),
        legend.background = element_rect(colour ="black"),
        panel.spacing = unit(1, "lines"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank()) +
  facet_grid(.~freq, scales = "free", labeller=freq_labels) -> p1

gamma_results %>% 
  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
  filter(homeo == "Homeostasis") %>% 
  group_by(freq, osc_rate, kind) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=kind)) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=kind), size=.4) +
  theme_classic() +
  facet_grid(.~freq, scales = "free", labeller = freq_labels) +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  lims(y=c(0.0, .12)) +
  theme(legend.position = "none",
        plot.tag = element_text(size=16, face="bold"),
        panel.spacing = unit(1, "lines"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank()) +
  labs(y="Kappa", x="Osc. rate", tag="b.") -> p2

@@

# Figure: Control
```{r, fig.width=5, fig.height=3.6}
# -
results228 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate, Ca_target) %>% 
  summarise(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp1

@@

# -----------------------------------------------------------------------------------
# Frac of tau_h
# rate
rbind(results231, results232) %>% 
  ggplot(aes(x=frac_tau_h, y=rate_k, color=homeo, group=interaction(homeo, frac_tau_h))) +
  geom_boxplot(size=0.6) +
  stat_compare_means(method="wilcox.test", label="p.signif", 
                     label.x=1.3, size=3, show.legend=FALSE) +
  labs(tag="c.", y="Pop. rate", x=TeX("$t_{oscillation} / \\tau_{h}$")) +
  scale_color_manual(values=c("black", "grey"), name=NA) +
  theme_classic2() +
  theme(
    plot.tag = element_text(size=18, face="bold"),
    legend.background = element_rect(colour ="black"),
    legend.position = c(1.35, 0.5),
    legend.title=element_blank(),
    legend.key.size = unit(.3, "cm")) -> p6

# -----------------------------------------------------------------------------------
# Freq Theta drift
results_control_drift %>% 
  filter(homeo=="Homeostasis") %>% 
  group_by(osc_rate, freq) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=as.factor(freq))) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=as.factor(freq)), size=.4) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  theme_classic() +
  labs(tag="d.", y="Pop. rate", x="Osc. rate") +
  lims(y=c(0.0, 100.0)) +
  theme(
    legend.position = c(1.35, -0.4),
    legend.key.size = unit(.4, "cm"),
    legend.background = element_rect(colour ="black"),
    plot.tag = element_text(size=18, face="bold")) +
  scale_color_manual(
    values=c("darkslategray3", "darkslategray4", "black", "darkolivegreen4", "darkolivegreen3"), 
    name="Freq. (Hz)") -> p10

results_control_drift %>% 
  filter(homeo=="Homeostasis") %>% 
  group_by(osc_rate, freq) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=as.factor(freq))) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=as.factor(freq)), size=.4) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  theme_classic() +
  labs(tag="e.", y="Kappa", x="Osc. rate") +
  lims(y=c(0.0, 0.2)) +
  theme(legend.position = "none",
        plot.tag = element_text(size=18, face="bold")) +
  scale_color_manual(
    values=c("darkslategray3", "darkslategray4", "black", "darkolivegreen4", "darkolivegreen3"), 
    name="Freq. (Hz)") -> p11

# -----------------------------------------------------------------------------------
results_control_leak %>% 
  filter(homeo=="Homeostasis") %>% 
  group_by(osc_rate, homeo, g_L) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=g_L)) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=g_L), size=.4) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  theme_classic() +
  theme(
    legend.position = c(1.4, -0.4),
    legend.key.size = unit(.4, "cm"),
    legend.background = element_rect(colour ="black"),
    plot.tag = element_text(size=18, face="bold")) +
  labs(tag="f.", y="Pop. rate", x="Osc. rate") +
  scale_color_manual(
    values=c("darkorange3", "darkorange4", "black", "gold4", "gold3"), 
    name="g_L (siemens)") -> p14

results_control_leak %>% 
  filter(homeo=="Homeostasis") %>% 
  group_by(osc_rate, homeo, g_L) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=g_L)) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=g_L), size=.4) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  theme_classic() +
  theme(legend.position = "none",
        plot.tag = element_text(size=18, face="bold")) +
  labs(tag="g.", y="Kappa", x="Osc. rate") +
  theme(plot.tag = element_text(size=16, face="bold")) + 
  scale_color_manual(
    values=c("darkorange3", "darkorange4", "black", "gold4", "gold3"), 
    name="g_L (siemens)") -> p15

# -----------------------------------------------------------------------------------
p3 <- textGrob("")
p4 <- textGrob("Target [Ca]\nperturbation")
p8 <- textGrob(TeX("Biological $\\tau_h$"))
p5 <- nullGrob()
p9 <- nullGrob()
p12 <- textGrob("Theta drift")
p13 <- textGrob("Conductance\nperturbation")

layout_matrix <- rbind(
  c(4, 2, 2, 5, 12, 10, 10, 9), 
  c(4, 2, 2, 5, 12, 10, 10, 9), 
  c(4, 2, 2, 5, 12, 10, 10, 9), 
  c(4, 2, 2, 5, 12, 10, 10, 9), 
  c(3, 1, 1, 5, 9,  11, 11, 9), 
  c(3, 1, 1, 5, 9,  11, 11, 9), 
  c(3, 1, 1, 5, 9,  11, 11, 9),  
  c(3, 1, 1, 9, 9,  11, 11, 9), 
  c(8, 6, 6, 9, 13, 14, 14, 9),
  c(8, 6, 6, 9, 13, 14, 14, 9),
  c(8, 6, 6, 9, 13, 14, 14, 9),
  c(8, 6, 6, 9, 13, 14, 14, 9),
  c(9, 9, 9, 9, 9,  15, 15, 9),
  c(9, 9, 9, 9, 9,  15, 15, 9),
  c(9, 9, 9, 9, 9,  15, 15, 9),
  c(9, 9, 9, 9, 9,  15, 15, 9)
)
grid.arrange(p1, p2, p3, p4, p5, p6, p8, p9, p10, p11, p12, p13, p14, p15, layout_matrix=layout_matrix)
